---
title: "HairSolon"
author: "Jerry Olsson"
date: "June 20, 2018"
output: html_document
---

Dataset description
Dataset: hairsalon.dat

Source: D. H. Dean (2012). "Gender, Ethnic Identity and Patronage Likelihood
for a Unisex Hair Salon," Young Consumers, Vol. 13, #2, pp. 124-135

Description: Patronage likelihoods among students exposed to an ad for a unisex hair salon by ethnicity and gender. Ratings on scale of 1-9.

Variables/Columns
Group         8   /* 1=W/M 2=W/F, 3=non-W/M, 4=non-W/F  */
Ehtnicity    16   /* 1=White,  2=non-White   */
Gender       24   /* 1=Male, 2=Female   */
Patronage likelihood     32 (out of 10)

# Group nominal categorical variable four values
# Ethnicity dichotomous categorical variable
# Gender dichotomous categorical variable
# Patronage Likelihood nominal categorical variable nine values
# Group, Ethnicity, Gender Independent Variables
# Patronage Likelihood Dependent Variable
Let's load some data
```{r}
salon <- read.table("C:/Users/rolsson/Desktop/SalonData.txt")
```

Let's load some libraries
```{r}
library(ggplot2)
```

Add Column heders to og data
```{r}
names(salon) <- c("Group", "Ethnicity", "Gender", "Patronage Likelihood")
```

EDA # Exploratory Data Anaylysis
```{r}
A <- salon$Ethnicity[salon$Ethnicity == 1]
length(A)
B <- salon$Ethnicity[salon$Ethnicity == 2]
length(B)
C <- salon$Gender[salon$Gender == 1]
length(C)
D <- salon$Gender[salon$Gender == 2]
length(D)
E <- salon$Group[salon$Group == 1]
length(E)
F <- salon$Group[salon$Group == 2]
length(2)
G <- salon$Group[salon$Group == 3]
length(G)
H <- salon$Group[salon$Group == 4]
length(H)
I <- salon$`Patronage Likelihood`[salon$`Patronage Likelihood` == 1]
length(I)
J <- salon$`Patronage Likelihood`[salon$`Patronage Likelihood` == 2]
length(J)
K <- salon$`Patronage Likelihood`[salon$`Patronage Likelihood` == 3]
length(K)
L <- salon$`Patronage Likelihood`[salon$`Patronage Likelihood` == 4]
length(L)
M <- salon$`Patronage Likelihood`[salon$`Patronage Likelihood` == 5]
length(M)
N <- salon$`Patronage Likelihood`[salon$`Patronage Likelihood` == 6]
length(N)
O <- salon$`Patronage Likelihood`[salon$`Patronage Likelihood` == 7]
length(O)
P <- salon$`Patronage Likelihood`[salon$`Patronage Likelihood` == 8]
length(P)
Q <- salon$`Patronage Likelihood`[salon$`Patronage Likelihood` == 9]
length(Q)
hist(salon$`Patronage Likelihood`)
```

boxplots
```{r}
boxplot(salon, data=salon, varwidth = TRUE)
```

